Refinement for open automata

### 2021-06-23 2021-Refinement/report.tex
Test fix for renaming, G3x not finished

\subsection{Properties of the relation on open automata}
The important properties we consider for a relation on open automata are:
\begin{defi} A relation \(\leq\) on open automata is
\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
\defitem \textbf{a preorder} iff it is reflexive and transitive;
\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\subst{b}{j} \leq a\);
\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\subst{c}{j}\);
\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\subst{c}{j} \leq b\subst{c}{j}\);
\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\subst{a}{j} \leq c\subst{b}{j}\);
\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\subst{a}{j} \leq d\subst{b}{j}\);
\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \cong b \wedge c \cong d \wedge a \leq c \implies b \leq d\).
\end{defi}
Reflexivity, transitivity and preorder are classical properties on relations.
Correctness w.r.t.\@ composition means that every composition is considered a refinement.
This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
Completeness w.r.t.\@ composition means that a refinement corresponds to the left automaton being equivalent to some composition of the right automaton.
This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
We won't have it because extending the domain of definition of the initial valuation will be a refinement which can't be expressed with composition.
Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
Context refinement is the refinement being compatible with composition of the same automaton.
Congruence is the refinement being compatible with being composed in the same automaton.
Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
This property is required on compositional structures to be of any use in verification, proofs and for model checking.
Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
Since FH-bisimulation is the pre-existing equivalence relation, we should not introduce an incompatible proof strategy.

@@

\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that

@@

	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}, more details on why the manipulations are possible are in the proof for transitivity of FH-bisimulation \cite{2007.10770}:

@@

		\iff & \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}

@@

% TODO: Renaming

@@

Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.

@@

Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
% END TODO

@@

	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).

@@

	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:

@@

		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
		\impliedby & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}

@@

		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}

@@

	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.

@@

% END TODO

@@

	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:

@@

		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}

@@

		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}

@@

		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.

@@

@@

Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_{x3}\).
% END TODO

@@

	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:

@@

		\impliedby & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}

@@

		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{4a} \\
		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{4b} \\
		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{4c}

@@

		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5} \\
		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6}
	We use \hyp{5} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5'} \]
	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6'} \]
	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.

@@

@@

Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_{x1}\).
% END TODO

@@

	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_1\) performs the same transition with same values in both composed automata:

@@

		\impliedby & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{12} = v_{13} \\
		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13}}
\item[\goal{1}:] Let \nmm{\sigma: V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \to \values}.
	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}} to get the left side of the implication (independent from these values), immediately broken into
		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{4a} \\
		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{4b} \\
		\sigma \vdash \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \hyp{4c}
	\(R_{23}\) is a simulation and \(\reach{A_{21}}\) is a witness of the non-locking composition so we have the hypotheses:
		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5} \\
		V_{21} \uplus \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6}
	We use \hyp{5} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \to \values}.
	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_3\) are still in transitions of \(A_{31}\), the right side gives:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5'} \]
	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}}.
	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6'} \]
	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.
\begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
\begin{proofsketch} The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient. \end{proofsketch}
With that last property, every interesting property is proved for the presented refinement relation.

>>>>

\subsection{Properties of the relation on open automata}
The important properties we consider for a relation on open automata are:
\begin{defi} A relation \(\leq\) on open automata is
\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
\defitem \textbf{a preorder} iff it is reflexive and transitive;
\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\subst{b}{j} \leq a\);
\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\subst{c}{j}\);
\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\subst{c}{j} \leq b\subst{c}{j}\);
\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\subst{a}{j} \leq c\subst{b}{j}\);
\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\subst{a}{j} \leq d\subst{b}{j}\);
\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \cong b \wedge c \cong d \wedge a \leq c \implies b \leq d\).
\end{defi}
Reflexivity, transitivity and preorder are classical properties on relations.
Correctness w.r.t.\@ composition means that every composition is considered a refinement.
This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
Completeness w.r.t.\@ composition means that a refinement corresponds to the left automaton being equivalent to some composition of the right automaton.
This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
We won't have it because extending the definition domain of the initial valuation will be a refinement which can't be expressed with composition.
Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
Context refinement is the refinement being compatible with composition of the same automaton.
Congruence is the refinement being compatible with being composed in the same automaton.
Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
This property is required on compositional structures to be of any use in verification, proofs and for model checking.
Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
Since FH-bisimulation is the pre-existing equivalence relation, we should not introduce an incompatible proof strategy.

@@

Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that

@@

	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\):

@@

		\iff & \mpar{R_{12}\mpar{s'_1, s'_2} \wedge R_{23}\mpar{s'_2, s'_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}
	Which is proved by \hyp{5d} and \hyp{6d}.
	The manipulations of substitutions are possible because their definition domain are disjoint; more details are available in the proof for transitivity of FH-bisimulation \cite{2007.10770}.

@@

@@

Let \(v_1 \mapsto v_{1'}\) be the renaming for \(v_1 \in V_1\) in \(A\).
Let \(\reach{A}\) be a witness that the composition \(A_1\subst{A_2}{k}\) is non-locking.

@@

@@

	We rename some variables in the definition domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).

@@

	For \goal{2d} we first perform a transformation.

@@

		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s'} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi_{1'} \uplus \psi_2 \uplus \psi_1} \\
		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s'}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1}}
	For the left side we use the preservation of reachability across transitions:
	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{2} \]
	\hyp{2} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{1a} and \hyp{1c}.
	For the right side, the variables of \(\psi\) are in \(V_1 \uplus \fvars{t_1}\) so proving the following is sufficient:
	\[ \sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \goal{2d'} \]
	By renaming of the definition domain, \(\nu\) coincides with \(\sigma\) on \(\fvars{t_1}\).
	For the other variables we use \hyp{1b}.

@@

		\sigma \vdash \reach{A}\mpar{s} \hyp{3a} \\
		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{3b} \\
		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3c}

@@

	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4} \]
	We use \hyp{4} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
	The left side of the implication is proved with \hyp{3a} and \hyp{3c}, the right side gives the hypothesis:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4'} \]
	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{4'}.

@@

@@

	For \goal{2d} we first perform a transformation.

@@

		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s'}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}}
	The left side is \hyp{4d}.
	For the right side we use the preservation of reachability across transitions:
	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{5} \]
	\hyp{5} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{3b} and \hyp{3c}.

@@

		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{6a} \\
		\sigma \vdash \reach{A}\mpar{s} \hyp{6b} \\
		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6c}

@@

		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8}
	We use \hyp{7} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
	The left side of the implication is proved with \hyp{6a} and \hyp{6c}, the right side gives the hypothesis:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7'} \]
	We then use \hyp{8} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
	The left side of the implication is proved using \hyp{6b} and \hyp{7'}, the right side gives:
	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8'} \]
	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{8'}.

@@

Let \(v_3 \mapsto v_{3x}\) is the renaming for \(v_3 \in V_3\) in \(A_{x3}\).

@@

@@

	For \goal{3d} we first perform a transformation.

@@

		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}}}
	The left side is \hyp{3d}.
	For the middle part we use the preservation of reachability across transitions:
	\[ \forall t_{13} \defobject \OTx{13}{}{13}{13} \in T_{13}, \fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \hyp{4} \]
	\hyp{4} is used for transition \(t_{13}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.

	For the right side, the variables of \(\psi_{13}\) and \(\psi_{23}\) are renaming of \(\psi_3\) on variables in \(\fvars{t_3}\) or do not involve these variables at all, so either \hyp{2c} is sufficient, or additionnaly proving the following is sufficient:
	\[ \nu' \vdash \bigwedge_\subbox{v_3 \in \fvars{t_3}} v_{31} = v_{32} \]
	Which holds by definition of \(\nu'\).

@@

		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}

@@

		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.

@@

Let \(v_1 \mapsto v_{1x}\) is the renaming for \(v_1 \in V_1\) in \(A_{x1}\).

@@

@@

	For \goal{3d} we first perform a tranfsformation.

@@

		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}}}
	The left side is \hyp{3d}.
	For the middle part we use the preservation of reachability across transitions:
	\[ \forall t_{21} \defobject \OTx{21}{}{21}{21} \in T_{21}, \fvars{t_{21}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge g_{21} \implies \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \hyp{4} \]
	\hyp{4} is used for transition \(t_{21}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.
